The College Application Problem

### 2022-05-10 paper.tex
new reference in introduction; formatting and style in slides

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror those for the knapsack problem: When each $g_j = 1$, the optimal portfolios are nested. This special case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offer any performance guarantee. However, we identify a fully polynomial-time approximation scheme (FPTAS) based on fixed-point arithmetic. 
%Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and a fully polynomial-time approximation scheme (FPTAS). We also describe a simulated-annealing algorithm that performs well in test instances. 
\else
탐욕 알고리즘이 좋은 근사해거나 정확한 알고리즘이 되는 최적화 모형들이 알려져 있다. 집합 크기 제약 하에서 submodular한 집합 함수를 최대화하는 문제가 대표적인 예다 (Fisher 외 1978). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 최적과 거리가 먼 해를 출력하는 예를 만들 수 있다 (Vazirani 2001). 대학 지원 문제와 배낭 문제가 서로 매우 유사함을 보인다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 증명한다. 이 경우는 지원 비용이 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 그러나 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘이 어떤 근사 계수를 보장할 수 없을 보일 수 있다. 대신 고정소숫점 산술을 활용한 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS)을 제시한다.
%대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS)을 제시한다. 가상 인스턴스에 성능이 좋은 모의 담금질(simulated annealing) 해법도 서술한다. 
\fi

@@

>>>>

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978; Assad 1985). For other problems, notably the binary knapsack problem, the most obvious greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror those for the knapsack problem: When each $g_j = 1$, the optimal portfolios are nested. This special case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offer any performance guarantee. Instead, we identify a fully polynomial-time approximation scheme (FPTAS) based on fixed-point arithmetic. 
%Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and a fully polynomial-time approximation scheme (FPTAS). We also describe a simulated-annealing algorithm that performs well in test instances. 
\else
탐욕 알고리즘이 좋은 근사해거나 정확한 알고리즘이 되는 최적화 모형들이 알려져 있다. 집합 크기 제약 하에서 submodular한 집합 함수를 최대화하는 문제가 대표적인 예다 (Fisher 외 1978; Assad 1985). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 최적과 거리가 먼 해를 출력하는 예를 만들 수 있다 (Vazirani 2001). 대학 지원 문제와 배낭 문제가 서로 매우 유사함을 보인다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 증명한다. 이 경우는 지원 비용이 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 그러나 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘이 어떤 근사 계수를 보장할 수 없을 보일 수 있다. 대신 고정소숫점 산술을 활용한 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS)을 제시한다.
%대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS)을 제시한다. 가상 인스턴스에 성능이 좋은 모의 담금질(simulated annealing) 해법도 서술한다. 
\fi

@@

Assad, Arjang. 1985. ``Nested Optimal Policies for Set Functions with Applications to Scheduling.'' \emph{Mathematics of Operations Research} 10 (1): 82--99.

### 2022-05-10 slides_08min/slides.tex
new reference in introduction; formatting and style in slides

\ifen {
\begin{frame}{Conclusion}
``Maximax'' form, integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack (cf. Fisher et al. 1978, Kulik et al. 2013).

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, FPTAS memory-usage improvements.
\end{frame}
} \else {
\begin{frame}{결론}
``Maximax'' 형태와 정수 조건 때문에 대학 지원 문제는 \textbf{이론적인 흥미가 깊다}. Submodular 최대화 문제지만, 근사 해법의 성질은 배낭 문제에 더 가깝다 (cf. Fisher et al. 1978, Kulik et al. 2013).

@@

\begin{frame}{\ifen References \else 참고 문헌 \fi}
\parskip 0em
\leftskip 2em
\parindent -2em
%Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.

@@

>>>>

\ifen {
\begin{frame}{Conclusion}
``Maximax'' form, integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack (cf.~Fisher et al. 1978; Kulik et al. 2013; Kellerer et al. 2004).

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, FPTAS memory-usage improvements.
\end{frame}
} \else {
\begin{frame}{결론}
\looseness=-1
``Maximax'' 형태와 정수 조건 때문에 대학 지원 문제는 \textbf{이론적인 흥미가 깊다}. Submodular 최대화 문제지만, 근사 해법의 성질은 배낭 문제에 더 가깝다 (cf. Fisher et al. 1978; Kulik et al. 2013; Kellerer et al. 2004).

@@

\begin{frame}{\ifen References \else 참고 문헌 \fi}
\small
\parskip 0em
\leftskip 2em
\parindent -2em
%Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.

@@

Kellerer, Hans, Ulrich Pferschy, and David Pisinger. 2004. \emph{Knapsack Problems.} Berlin: Springer.

### 2022-05-10 slides_20min/slides.tex
new reference in introduction; formatting and style in slides

발표 요약:
\begin{itemize}
\item 대학 지원 전략을 최적화 문제로 \textbf{모형화}.
\item \textbf{현재 상황}: 입학 컨설팅 산업에서 흔히 사용하는 휴리스틱의 부족함.
\item 본 연구가 제시하는 \textbf{이론적 결과, 해법, 알고리즘 구현}.
\end{itemize}
\end{frame}
} \fi

@@

Given a student's academic records, test scores, and demographic information, we can estimate her \textbf{admissions probability} $f_j$ at each school.

@@

학생의 내신, 수능 점수, 기본 정보가 주어지면 각 학교의 \textbf{합격 확률} $f_j$를 추정할 수 있다.

\mbox{독립한 \textbf{확률 변수} $Z_j \sim \operatorname{Bernoulli}(f_j)$는 학생이 합격하면 $1$, 아니면 $0$.}

\mbox{학생이 지원하는 학교의 집합 $\mathcal{X} \subseteq \mathcal{C}$를 \textbf{지원 포트폴리오}라고 부른다.}

@@

￣

@@

Our algorithms provide both \textbf{time and accuracy guarantees}. 
\end{frame}
} \else {
\begin{frame}{기존의 해법}
입학 컨설팅 산업에서는 주로 ``상향·소신·안정 지원 학교'' 각각 균일하게 지원하는 \textbf{배분적 휴리스틱}을 권장하며, 이는 \textbf{위험 회피적인} 전략임을 알 수 있다.

@@

Fisher et al. (1978)에 결과를 강화한다.
\end{frame}
} \fi

@@

FPTAS의 존재성은 대학 지원 문제가 \textbf{submodular 최대화의 비교적 쉬운 인스턴스}임을 의미한다 (cf. Kulik et al. 2013).
\end{frame}
} \fi

@@

\ifen {
\begin{frame}[plain]
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
\end{center}
\end{frame}
} \else {
\begin{frame}[plain]
  \vfill
\begin{center}
~
\begin{beamercolorbox}[wd=.5\textwidth,sep=8pt,center,shadow=false,rounded=true]{section in head/foot}
    \usebeamerfont{title} \insertsectionhead
  \end{beamercolorbox}
\end{center}
\end{frame}
} \fi

\ifen {
\begin{frame}{Conclusion}
``Maximax'' form, integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack (cf. Fisher et al. 1978, Kulik et al. 2013).

The nestedness result for the $g_j = 1$ special case also resembles the knapsack problem, although the proof is more subtle.

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, FPTAS memory-usage improvements.
\end{frame}
} \else {
\begin{frame}{결론}
``Maximax'' 형태와 정수 조건 때문에 대학 지원 문제는 \textbf{이론적인 흥미가 깊다}. Submodular 최대화 문제지만, 근사 해법의 성질은 배낭 문제에 더 가깝다 (cf. Fisher et al. 1978, Kulik et al. 2013).

$g_j=1$의 특수한 경우의 포함 사슬 관계 성질도 배낭 문제와 유사하며, 증명 과정은 좀 더 미묘하다.

@@

\begin{frame}{\ifen References \else 참고 문헌 \fi}
\small
\parskip 0em
\leftskip 1.5em
\parindent -1.5em
%Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.

@@

@@

\begin{frame}{\ifen Appendix: Summary of algorithms\else 부록: 알고리즘 요약\fi}
\begin{center}
\ifen
\scalebox{0.90}{ 
\begin{tabular}{r|lllll}
\textbf{Algorithm} & \textbf{Problem} & \textbf{Restrictions} & \textbf{Exactness}       & \textbf{Computation time} \\ \hline
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Na\"ive\end{tabular} &  \begin{tabular}[l]{@{}l@{}}Homogeneous \\ costs\end{tabular}     & None                  & $(1/h)$-opt.               & $O(m)$                    \\ 
\xrowht[()]{1.5em}  Greedy                &   \begin{tabular}[l]{@{}l@{}}Homogeneous \\ costs\end{tabular}    & None                  & Exact                    & $O(hm)$                   \\
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Branch and\\ bound\end{tabular}   & General          & None                  & Exact                    & $O(2^m)$                  \\
\xrowht[()]{1.5em}  Costs DP     &   General          & $g_j$ integer         & Exact                    & $O(Hm + m \log m)$        \\
\xrowht[()]{1.5em}  FPTAS      &   General          & None        & $(1 - \varepsilon)$-opt. & $O(m^3 / \varepsilon)$   \\
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Simulated\\annealing\end{tabular}   & General          & None                  & $0$-opt.                    & $O(Nm)$                
\end{tabular}
}
\else
\scalebox{1}{ 
\begin{tabular}{r|lllll}
\textbf{알고리즘} &  \textbf{문제} & \textbf{제한} & \textbf{정확도}       & \textbf{계산 시간} \\ \hline
\xrowht[()]{1.7em}  \begin{tabular}[r]{@{}r@{}}나이브\end{tabular}                & \begin{tabular}[l]{@{}l@{}}동일한\\ 지원 비용\end{tabular}     & 없음                  & $(1/h)$-근사          & $O(m)$                    \\ 
\xrowht[()]{1.7em}  탐욕 해법               &  \begin{tabular}[l]{@{}l@{}}동일한\\ 지원 비용\end{tabular}    & 없음                  & 정확                    & $O(hm)$                   \\
\xrowht[()]{1.7em}  \begin{tabular}[r]{@{}r@{}}분지한계법\end{tabular}   & 일반 문제          & 없음                  & 정확                    & $O(2^m)$                  \\
\xrowht[()]{1.7em}   \begin{tabular}[r]{@{}r@{}}지출액\\ 동적 계획\end{tabular}    & 일반 문제          & $g_j$ 정수         & 정확                    & $O(Hm + m \log m)$        \\
\xrowht[()]{1.7em}  FPTAS       & 일반 문제          & 없음        & $(1 - \varepsilon)$-근사 & $O(m^3 / \varepsilon)$   \\
\xrowht[()]{1.7em}   \begin{tabular}[r]{@{}r@{}}모의\\ 담금질\end{tabular}    & 일반 문제          & 없음                      & $0$-근사                    & $O(Nm)$                
\end{tabular}
}
\fi
\end{center}
\end{frame}

>>>>

발표 요약:
\begin{itemize}
\item 대학 지원 전략을 최적화 문제로 \textbf{모형화}.
\item \textbf{현재 상황}: 입학 컨설팅 산업에서 흔히 사용하는 휴리스틱의 부족함.
\item 본 연구가 제시하는 \textbf{이론적 결과, 해법, 그리고 알고리즘 구현}.
\end{itemize}

\mbox{\textbf{발표에서 생략된 증명 등}은 arXiv 논문에서 제시 (Kapur와 Hong 2022).}
\end{frame}
} \fi

@@

Given a student's academic records, test scores, and demographic information, we can determine her \textbf{admissions probability} $f_j$ at each school.

@@

학생의 내신, 수능 점수, 기본 정보가 주어지면 각 학교의 \textbf{합격 확률} $f_j$를 알 수 있다.

\looseness=-1
독립한 \textbf{확률 변수} $Z_j \sim \operatorname{Bernoulli}(f_j)$는 학생이 합격하면 $1$, 아니면 $0$.

\looseness=-1
학생이 지원하는 학교의 집합 $\mathcal{X} \subseteq \mathcal{C}$를 \textbf{지원 포트폴리오}라고 부른다.

@@

@@

Our algorithms provide both \textbf{time and accuracy guarantees}. 
\end{frame}
} \else {
\begin{frame}{기존의 해법}
입학 컨설팅 산업에서는 주로 ``상향·소신·안정 지원 학교'' 각각 균일하게 지원하는 \textbf{배분적 휴리스틱}을 권장하며, 이는 \textbf{위험 회피적인} 전략임을 보일 수 있다.

@@

Fisher 외 (1978)의 결과를 강화한다.
\end{frame}
} \fi

@@

FPTAS의 존재성은 대학 지원 문제가 \textbf{submodular 최대화의 비교적 쉬운 인스턴스}임을 의미한다 (cf. Kulik 외 2013).
\end{frame}
} \fi

@@

\ifen {
\begin{frame}{Conclusion}
``Maximax'' form, integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack (cf.~Fisher et al. 1978; Kulik et al. 2013; Kellerer et al. 2004).

% I decided I don't like this sentence bc the claim is obvious and the claim that the proof is ``subtle'' is subjective.
%The nestedness result for the $g_j = 1$ special case also resembles the knapsack problem, although the proof is more subtle.

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, FPTAS memory-usage improvements.
\end{frame}
} \else {
\begin{frame}{결론}
\looseness=-1
``Maximax'' 형태와 정수 조건 때문에 대학 지원 문제는 \textbf{이론적인 흥미가 깊다}. Submodular 최대화 문제지만, 근사 해법의 성질은 배낭 문제에 더 가깝다 (cf. Fisher 외 1978; Kulik 외 2013; Kellerer 외 2004).

%$g_j=1$의 특수한 경우의 포함 사슬 관계 성질도 배낭 문제와 유사하며, 증명 과정은 좀 더 미묘하다.

@@

\begin{frame}[allowframebreaks]{\ifen References \else 참고 문헌 \fi}
\parskip 0em
\leftskip 2em
\parindent -2em
%Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.

@@

\framebreak

Kellerer, Hans, Ulrich Pferschy, and David Pisinger. 2004. \emph{Knapsack Problems.} Berlin: Springer.

@@

\begin{frame}{\ifen Appendix: Summary of algorithms\else 부록: 알고리즘 요약\fi}
\begin{center}
\ifen
\scalebox{0.90}{ 
\begin{tabular}{r|lllll}
\textbf{Algorithm} & \textbf{Problem} & \textbf{Restrictions} & \textbf{Exactness}       & \textbf{Computation time} \\ \hline
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Na\"ive\end{tabular} &  \begin{tabular}[l]{@{}l@{}}Homogeneous \\ costs\end{tabular}     & None                  & $(1/h)$-opt.               & $O(m)$                    \\ 
\xrowht[()]{1.5em}  Greedy                &   \begin{tabular}[l]{@{}l@{}}Homogeneous \\ costs\end{tabular}    & None                  & Exact                    & $O(hm)$                   \\
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Branch and\\ bound\end{tabular}   & General          & None                  & Exact                    & $O(2^m)$                  \\
\xrowht[()]{1.5em}  Costs DP     &   General          & $g_j$ integer         & Exact                    & $O(Hm + m \log m)$        \\
\xrowht[()]{1.5em}  FPTAS      &   General          & None        & $(1 - \varepsilon)$-opt. & $O(m^3 / \varepsilon)$   \\
\xrowht[()]{1.5em}  \begin{tabular}[r]{@{}r@{}}Simulated\\annealing\end{tabular}   & General          & None                  & $0$-opt.                    & $O(Nm)$                
\end{tabular}
}
\else
\scalebox{1}{ 
\begin{tabular}{r|lllll}
\textbf{알고리즘} &  \textbf{문제} & \textbf{제한} & \textbf{정확도}       & \textbf{계산 시간} \\ \hline
\xrowht[()]{1.7em}  \begin{tabular}[r]{@{}r@{}}나이브\end{tabular}                & \begin{tabular}[l]{@{}l@{}}동일한\\ 지원 비용\end{tabular}     & 없음                  & $(1/h)$-근사          & $O(m)$                    \\ 
\xrowht[()]{1.7em}  탐욕 해법               &  \begin{tabular}[l]{@{}l@{}}동일한\\ 지원 비용\end{tabular}    & 없음                  & 정확                    & $O(hm)$                   \\
\xrowht[()]{1.7em}  \begin{tabular}[r]{@{}r@{}}Branch and\\ bound\end{tabular}   & 일반 문제          & 없음                  & 정확                    & $O(2^m)$                  \\
\xrowht[()]{1.7em}   \begin{tabular}[r]{@{}r@{}}지원 비용\\ 동적 계획\end{tabular}    & 일반 문제          & $g_j$ 정수         & 정확                    & $O(Hm + m \log m)$        \\
\xrowht[()]{1.7em}  FPTAS       & 일반 문제          & 없음        & $(1 - \varepsilon)$-근사 & $O(m^3 / \varepsilon)$   \\
\xrowht[()]{1.7em}   \begin{tabular}[r]{@{}r@{}}Simulated\\ annealing\end{tabular}    & 일반 문제          & 없음                      & $0$-근사                    & $O(Nm)$                
\end{tabular}
}
\fi
\end{center}
\end{frame}
